### 2018-11-15 arxiv/introduction.tex
arvix - getting rid of references to appendices (aside of A, using references here)
Minor edits. Reworded a few sentences

Several VQA datasets have been proposed (e.g. DAQUAR~\cite{malinowski2014multi}, VQA~\cite{antol2015vqa}); nonetheless, these datasets contain several biases (e.g. unbalanced questions or answers) that are often exploited by systems during learning~\cite{goyal2017making}.
The CLEVR dataset~\cite{johnson2017clevr} was designed to address these issues. The synthetic nature of its images \& questions enables detailed analysis of visual reasoning, and allows for variations, to test a particular ability such as generalization or transfer learning. One variation of CLEVR, called CoGenT (Compositional Generalization Test), measures whether models learn separate representations for color and shape instead of memorizing all possible combinations. 
For details, see Appendix~A (all appendices in supplementary material).

@@

>>>>

Several VQA datasets have been proposed (e.g. DAQUAR~\cite{malinowski2014multi}, VQA~\cite{antol2015vqa}); nonetheless, these datasets contain several biases (e.g. unbalanced questions or answers) that are often exploited by systems during learning~\cite{goyal2017making}.
The CLEVR dataset~\cite{johnson2017clevr} was designed to address these issues. The synthetic nature of its images \& questions enables detailed analysis of visual reasoning, and allows for variations, to test a particular ability such as generalization or transfer learning. One variation of CLEVR, called CoGenT (Compositional Generalization Test), measures whether models learn separate representations for color and shape instead of memorizing all possible combinations.

@@

The paper is organized as follows.
In \sec{datasets} we delve into details of both CLEVR and CoGenT datasets, emphasizing their differences.
Next, in \sec{models}) we present both MAC and S-MAC models and explain what motivated the formulation of equations for the latter.
\sec{experiments} discusses the most important results of using transfer learning 
on CLEVR and on both versions of CoGenT.
\sec{transfer_learning} focuses on a cherry-picked subset of experiments to highlight our findings; 
see~Appendix~\ref{sec:full_comparison} for the complete set of results comparing MAC and S-MAC models when training/fine-tuning/testing on various datasets.
In \sec{failures} we present examples that support hypothesis on the lack of disentanglement of concepts in both models.
\sec{comparison} presents results obtained by other state-of-the-art models, and discusses the challenges faced  
with their reproducibility. 
\sec{conclusion} concludes the paper.
